### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of cache line instead of a cache set. While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory,
who may load the sensitive information to the cache line. On X86-64 machines, it can be achieved by using the \textsf{clflush} instruction. In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time difference
brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
layers other than CPU cache.

>>>>

\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of cache line instead of a cache set. While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
memory'' from the cache and waits for the victim to access the memory, who may load the sensitive information to the cache line.  In the next phase,
the attacker reloads the ``monitored memory''. By measuring the time differences
brought by cache hits and misses, the attacker can further infer the sensitive information. On X86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.

Some other types of side-channels target different hardware layers other than CPU cache.
